Efficiency

### 2018-01-08 DraftExec.Rnw
bump

Para

@@

The selection of the DCNS bid to design the future submarine attracted considerable attention and controversy on a number of fronts. The choice of the pumpjet, and the question of efficiency at low speeds, has been touched on briefly in various informed discussions \parencite{stanford2017} \parencite{davies2017}.  However, it has remained the case that even extremely well-informed commentators reluctant to quantify and qualify the plausible scale of this trade-off, and what it might mean strategically and tactically for the submarine. Everyone knew it was an issue, but no-one confident enough in the scale (or even direction \parencite{davies2017}) of the impact to make it clear whether it mattered. Even the head of the progam to build the submarine acknowledged an improvement in dived endurance might be possible with conventional propellers \parencite{sbs2017}, which seemed a clear acknowledgment that some trade-off was acknowledged, even by the strongest advocates of the pumpjet.

@@

The conclusion of the analysis, and the plotting of these results for certain possible values of $K$ and $\Delta T$ is: "Its outstanding characteristic is that this efficiency approaches zero rather than unity for $\Delta V / V_0 = 0$, even for small duct losses".

@@

\subsection{The impact of duct shielding}
The presence of the duct around the impeller may also have the effect of preventing the noise from being effectively radiated away from the propulsor.  This may well result in substantial reductions in some types of noise being radiated away from the propulsor in certain directions, which may have given rise to the consistent qualification of 'radiated' being used to descrive the type of noise which differentiated the French submarine bid \parencite{stewart2016, davies2017, ohff2016}, including by the designers of the submarine \parencite{autret2016}.  This is a secondary effect, quite separate to the avoidance of cavitation, which might be seen as an acoustic advantage in circumstances where cavitation might not be expected to occur on either type of propulsor.  It is highly likely that this is the effect which is relied upon to sustain claims that a pumpjet is generally acoustically superior to a propeller, including at low speeds.

>>>>

@@

The selection of the DCNS bid to design the future submarine attracted considerable attention and controversy on a number of fronts. The choice of the pumpjet, and the question of efficiency at low speeds, has been touched on briefly in various informed discussions (\cite{stanford2017}, \cite{davies2017}).  However, it has remained the case that even extremely well-informed commentators reluctant to quantify and qualify the plausible scale of this trade-off, and what it might mean strategically and tactically for the submarine. Everyone knew it was an issue, but no-one confident enough in the scale (or even direction \parencite{davies2017}) of the impact to make it clear whether it mattered. Even the head of the progam to build the submarine acknowledged an improvement in dived endurance might be possible with conventional propellers \parencite{sbs2017}, which seemed a clear acknowledgment that some trade-off was acknowledged, even by the strongest advocates of the pumpjet.

@@

The conclusion of the analysis, and the plotting of these results for certain possible values of $K$ and $\Delta T$ is: "Its outstanding characteristic is that this efficiency approaches zero rather than unity for $\Delta V / V_0 = 0$ , even for small duct losses".

@@

\subsection{The impact of duct shielding}
The presence of the duct around the impeller may also have the effect of preventing the noise from being effectively radiated away from the propulsor.  This may well result in substantial reductions in some types of noise being radiated away from the propulsor in certain directions, which may have given rise to the consistent qualification of 'radiated' being used to descrive the type of noise which differentiated the French submarine bid (\cite{stewart2016}, \cite{davies2017}, \cite{ohff2016}), including by the designers of the submarine \parencite{autret2016}.  This is a secondary effect, quite separate to the avoidance of cavitation, which might be seen as an acoustic advantage in circumstances where cavitation might not be expected to occur on either type of propulsor.  It is highly likely that this is the effect which is relied upon to sustain claims that a pumpjet is generally acoustically superior to a propeller, including at low speeds.
